In mammals, an important proportion of advantageous mutations are repairing damaged genomes instead of creating adaptive innovations

### 2022-09-15 manuscript/supp-mat.tex
Figure labels in Supp. Mat.
N. Salamin corrections
Added conditional probabilities

\newcommand{\UniDimArray}[1]{\bm{#1}}
\newcommand{\BiDimArray}[1]{\bm{#1}}
\DeclareMathOperator{\E}{\mathbb{E}}
\DeclareMathOperator{\Var}{\textrm{Var}}
\newcommand{\der}{\textrm{d}}
\newcommand{\e}{\textrm{e}}
\newcommand{\avg}[1]{\left< #1 \right>} % for average
\newcommand{\Ne}{N_{\textrm{e}}}
\newcommand{\proba}{\mathbb{P}}
\newcommand{\pfix}{\proba_{\textrm{fix}}}
\newcommand{\dn}{d_N}
\newcommand{\ds}{d_S}
\newcommand{\dnds}{\dn / \ds}
\newcommand{\Sphy}{S}
\newcommand{\Sphyclass}{\mathcal{C}}
\newcommand{\SphyMean}{\overline{\Sphy}}
\newcommand{\divStrongDel}{\Sphy < -3}
\newcommand{\divDel}{-3 < \Sphy < -1}
\newcommand{\divWeakDel}{-1 < \Sphy < 0}
\newcommand{\divWeakAdv}{0 < \Sphy < 1}
\newcommand{\divAdv}{ \Sphy > 1}
\newcommand{\PdivStrongDel}{\proba \left[ \divStrongDel \right]}
\newcommand{\PdivDel}{\proba \left[ \divDel \right]}
\newcommand{\PdivWeakDel}{\proba \left[ \divWeakDel \right]}
\newcommand{\PdivWeakAdv}{\proba \left[ \divWeakAdv \right]}
\newcommand{\PdivAdv}{\proba \left[ \divAdv \right]}

\newcommand{\Spop}{\beta}
\newcommand{\SpopMean}{\overline{\Spop}}
\newcommand{\polyDel}{\Spop < -1}
\newcommand{\polyNeutral}{-1 < \Spop < 1}
\newcommand{\polyAdv}{ \Spop > 1}
\newcommand{\PpolyDel}{\proba \left[ \polyDel \right]}
\newcommand{\PpolyNeutral}{\proba \left[ \polyNeutral \right]}
\newcommand{\PpolyAdv}{\proba \left[ \polyAdv \right]}

\title{In mammals, 20 to 40\% of advantageous mutations are restoring damaged genomes instead of creating adaptive innovations}

\author{
    \large
    \textbf{T. {Latrille}$^{1}$, J. {Joseph}$^{2}$, N. {Salamin}$^{1}$}\\
    \normalsize $^{1}$Université de Lausanne, Lausanne, Switzerland\\
    \normalsize $^{2}$Université de Lyon, Lyon, France \\
    \normalsize \texttt{\href{mailto:thibault.latrille@ens-lyon.org}{thibault.latrille@ens-lyon.org}} \\
}

@@

    \subsection{Summary tables}\label{subsec:summary-table-mutsel}
    \begin{center}
        \captionof{table}{~}
        \scriptsize
        \begin{longtable*}{|l|l|r|r|r|r|r|r|}
            \toprule
            Population           & Species             & Tajima $\theta$ & $\mathbb{P} [ \Spop > 1 ]$ & $\mathbb{P}_{mut}[\Sphy > 1]$ & $\mathbb{P} [ \Spop > 1  | \Sphy > 1]$ & $\mathbb{P}_{div}[\Sphy > 1]$ & $\dn(\Sphy > 1) / \ds$ \\
            \midrule
            \endhead
            \midrule
            \multicolumn{8}{r}{{Continued on next page}} \\
            \midrule
            \endfoot

@@

            Equus c.             & Equus caballus      & $ 0.002$        & $ 0.042$                   & $ 0.018$                      & $ 0.404$                             & $ 0.115$                      & $ 1.197$           \\
            Iran                 & Bos taurus          & $ 0.005$        & $ 0.036$                   & $ 0.017$                      & $ 0.368$                             & $ 0.125$                      & $ 1.322$           \\
            Uganda               & Bos taurus          & $ 0.006$        & $ 0.035$                   & $ 0.017$                      & $ 0.369$                             & $ 0.126$                      & $ 1.363$           \\
            Australia            & Capra hircus        & $ 0.003$        & $ 0.036$                   & $ 0.017$                      & $ 0.144$                             & $ 0.122$                      & $ 1.035$           \\
            France               & Capra hircus        & $ 0.004$        & $ 0.034$                   & $ 0.017$                      & $ 0.168$                             & $ 0.122$                      & $ 1.043$           \\
            Iran (C. aegagrus)   & Capra hircus        & $ 0.004$        & $ 0.035$                   & $ 0.017$                      & $ 0.093$                             & $ 0.123$                      & $ 1.042$           \\
            Iran                 & Capra hircus        & $ 0.004$        & $ 0.030$                   & $ 0.017$                      & $ 0.140$                             & $ 0.124$                      & $ 1.052$           \\
            Italy                & Capra hircus        & $ 0.004$        & $ 0.032$                   & $ 0.017$                      & $ 0.150$                             & $ 0.122$                      & $ 1.037$           \\
            Morocco              & Capra hircus        & $ 0.004$        & $ 0.029$                   & $ 0.017$                      & $ 0.137$                             & $ 0.124$                      & $ 1.057$           \\
            Iran                 & Ovis aries          & $ 0.008$        & $ 0.022$                   & $ 0.018$                      & $ 0.046$                             & $ 0.104$                      & $ 1.180$           \\
            Iran (O. orientalis) & Ovis aries          & $ 0.009$        & $ 0.025$                   & $ 0.018$                      & $ 0.071$                             & $ 0.103$                      & $ 1.187$           \\
            Iran (O. vignei)     & Ovis aries          & $ 0.008$        & $ 0.028$                   & $ 0.018$                      & $ 0.220$                             & $ 0.104$                      & $ 1.172$           \\
            Various              & Ovis aries          & $ 0.009$        & $ 0.024$                   & $ 0.018$                      & $ 0.108$                             & $ 0.103$                      & $ 1.182$           \\
            Morocco              & Ovis aries          & $ 0.008$        & $ 0.020$                   & $ 0.018$                      & $ 0.070$                             & $ 0.104$                      & $ 1.189$           \\
            Barbados             & Chlorocebus sabaeus & $ 0.004$        & $ 0.040$                   & $ 0.015$                      & $ 0.374$                             & $ 0.123$                      & $ 1.341$           \\
            Central Afr. Rep.    & Chlorocebus sabaeus & $ 0.006$        & $ 0.034$                   & $ 0.015$                      & $ 0.368$                             & $ 0.124$ & $ 1.370$ \\
            Ethiopia             & Chlorocebus sabaeus & $ 0.005$        & $ 0.040$                   & $ 0.015$                      & $ 0.368$                             & $ 0.124$                      & $ 1.361$           \\
            Gambia               & Chlorocebus sabaeus & $ 0.005$        & $ 0.031$                   & $ 0.015$                      & $ 0.377$                             & $ 0.124$                      & $ 1.359$           \\
            Kenya                & Chlorocebus sabaeus & $ 0.006$        & $ 0.035$                   & $ 0.015$                      & $ 0.308$                             & $ 0.125$                      & $ 1.371$           \\
            Nevis                & Chlorocebus sabaeus & $ 0.004$        & $ 0.037$                   & $ 0.015$                      & $ 0.368$                             & $ 0.124$                      & $ 1.349$           \\
            South Africa         & Chlorocebus sabaeus & $ 0.007$        & $ 0.034$                   & $ 0.015$                      & $ 0.368$                             & $ 0.126$                      & $ 1.391$           \\
            Saint Kitts          & Chlorocebus sabaeus & $ 0.004$        & $ 0.039$                   & $ 0.015$                      & $ 0.368$                             & $ 0.125$                      & $ 1.362$           \\
            Zambia               & Chlorocebus sabaeus & $ 0.006$        & $ 0.038$                   & $ 0.015$                      & $ 0.368$                             & $ 0.124$                      & $ 1.362$           \\
            African              & Homo sapiens        & $ 0.003$        & $ 0.038$                   & $ 0.015$                      & $ 0.604$                             & $ 0.104$                      & $ 1.475$           \\
            Admixed American     & Homo sapiens        & $ 0.002$        & $ 0.037$                   & $ 0.015$                      & $ 0.574$                             & $ 0.103$                      & $ 1.466$           \\
            East Asian           & Homo sapiens        & $ 0.002$        & $ 0.036$                   & $ 0.015$                      & $ 0.484$                             & $ 0.104$                      & $ 1.478$           \\
            European             & Homo sapiens        & $ 0.002$        & $ 0.037$                   & $ 0.015$                      & $ 0.517$                             & $ 0.103$                      & $ 1.461$           \\
            South Asian          & Homo sapiens        & $ 0.002$        & $ 0.036$                   & $ 0.015$                      & $ 0.532$                             & $ 0.104$                      & $ 1.473$           \\

@@

        \item $\mathbb{P} [ \Spop > 1 ]$ is the probability of $\Spop > 1$ estimated by polyDFE from all SNPs.
        \item $\mathbb{P}_{mut}[\Sphy > 0]$ is the proportion of mutational opportunities with a predicted selection coefficient larger than 1 ($\Sphy > 1$).
        \item $\mathbb{P} [ \Spop > 1  | \Sphy > 1]$ is the probability of $\Spop > 1$ estimated by polyDFE for SNPs with a predicted selection coefficient larger than 1 ($\Sphy > 1$).
        \item $\mathbb{P}_{div}[\Sphy > 1]$ is the proportion of substitutions in the terminal branch observed with a selection coefficient at the phylogenetic scale larger than 1 ($\Sphy > 1$).
        \item $\dn(\Sphy > 1) / \ds$ is the ratio of non-synonymous over synonymous divergence (also called $\dnds$) estimated for the non-synonymous substitutions in the terminal branch with a selection coefficient larger than 1 ($\Sphy > 1$).

@@

    \newpage
    \begin{center}
        \captionof{table}{~}
        \scriptsize
        \begin{longtable*}{|l|l|r|r|r|r|r|r|r|r|}
            \toprule
            Population           & Species             & Tajima $\theta_{\pi}$ & $\mathbb{P}_{div}[\Sphy > 0]$ & $\dnds $ & $\dn(\Sphy < 0) / \ds$ & R($\dnds $) & $p_+ $ & $p_+(\Sphy < 0)$ & R($p_+ $) \\
            \midrule
            \endhead
            \midrule
            \multicolumn{9}{r}{{Continued on next page}} \\
            \midrule
            \endfoot
            Equus c.             & Equus caballus      & $ 0.002$              & $ 0.275$                      & $ 0.148$ & $ 0.113$     & $  23.4$      & $ 0.042$ & $ 0.030$ & $  28.5$ \\
            Iran                 & Bos taurus          & $ 0.005$              & $ 0.274$                      & $ 0.130$ & $ 0.100$     & $  23.3$      & $ 0.036$ & $ 0.025$   & $  30.9$    \\
            Uganda               & Bos taurus          & $ 0.006$              & $ 0.277$                      & $ 0.133$ & $ 0.101$     & $  23.6$      & $ 0.035$ & $ 0.023$   & $  33.7$    \\
            Australia            & Capra hircus        & $ 0.003$              & $ 0.286$                      & $ 0.126$ & $ 0.095$     & $  24.6$      & $ 0.036$ & $ 0.026$ & $  26.8$ \\
            France               & Capra hircus        & $ 0.004$              & $ 0.286$                      & $ 0.127$ & $ 0.096$     & $  24.6$      & $ 0.034$ & $ 0.025$ & $  26.7$ \\
            Iran (C. aegagrus)   & Capra hircus        & $ 0.004$              & $ 0.285$                      & $ 0.126$ & $ 0.095$     & $  24.5$      & $ 0.035$ & $ 0.026$ & $  25.0$ \\
            Iran                 & Capra hircus        & $ 0.004$              & $ 0.288$                      & $ 0.126$ & $ 0.095$     & $  24.8$      & $ 0.030$ & $ 0.020$   & $  31.8$    \\
            Italy                & Capra hircus        & $ 0.004$              & $ 0.287$                      & $ 0.127$ & $ 0.096$     & $  24.6$      & $ 0.032$ & $ 0.022$   & $  30.6$    \\
            Morocco              & Capra hircus        & $ 0.004$              & $ 0.288$                      & $ 0.126$ & $ 0.095$     & $  24.7$      & $ 0.029$ & $ 0.020$ & $  31.5$ \\
            Iran                 & Ovis aries          & $ 0.008$              & $ 0.243$                      & $ 0.149$ & $ 0.120$     & $  20.0$      & $ 0.022$ & $ 0.014$   & $  36.5$    \\
            Iran (O. orientalis) & Ovis aries          & $ 0.009$              & $ 0.241$                      & $ 0.151$ & $ 0.121$     & $  19.8$      & $ 0.025$ & $ 0.016$ & $  33.4$ \\
            Iran (O. vignei)     & Ovis aries          & $ 0.008$              & $ 0.243$                      & $ 0.149$ & $ 0.119$     & $  20.0$      & $ 0.028$ & $ 0.019$ & $  30.5$ \\
            Various              & Ovis aries          & $ 0.009$              & $ 0.240$                      & $ 0.151$ & $ 0.121$     & $  19.7$      & $ 0.024$ & $ 0.015$   & $  36.7$    \\
            Morocco              & Ovis aries          & $ 0.008$              & $ 0.241$                      & $ 0.151$ & $ 0.121$     & $  19.7$      & $ 0.020$ & $ 0.013$   & $  38.0$    \\
            Barbados             & Chlorocebus sabaeus & $ 0.004$              & $ 0.289$                      & $ 0.141$ & $ 0.106$     & $  25.1$      & $ 0.040$ & $ 0.030$ & $  25.3$ \\
            Central Afr. Rep.    & Chlorocebus sabaeus & $ 0.006$              & $ 0.287$                      & $ 0.141$ & $ 0.106$     & $  24.9$ & $ 0.034$ & $ 0.026$ & $  24.7$ \\
            Ethiopia             & Chlorocebus sabaeus & $ 0.005$              & $ 0.290$                      & $ 0.141$ & $ 0.105$     & $  25.2$      & $ 0.040$ & $ 0.030$ & $  25.0$ \\
            Gambia               & Chlorocebus sabaeus & $ 0.005$              & $ 0.287$                      & $ 0.141$ & $ 0.106$     & $  25.0$      & $ 0.031$ & $ 0.021$ & $  31.8$ \\
            Kenya                & Chlorocebus sabaeus & $ 0.006$              & $ 0.290$                      & $ 0.142$ & $ 0.106$     & $  25.2$      & $ 0.035$ & $ 0.026$ & $  24.9$ \\
            Nevis                & Chlorocebus sabaeus & $ 0.004$              & $ 0.289$                      & $ 0.141$ & $ 0.106$     & $  25.1$      & $ 0.037$ & $ 0.028$ & $  23.6$ \\
            South Africa         & Chlorocebus sabaeus & $ 0.007$              & $ 0.291$                      & $ 0.141$ & $ 0.105$     & $  25.4$      & $ 0.035$ & $ 0.025$ & $  27.7$ \\
            Saint Kitts          & Chlorocebus sabaeus & $ 0.004$              & $ 0.290$                      & $ 0.141$ & $ 0.105$     & $  25.3$      & $ 0.039$ & $ 0.029$ & $  26.1$ \\
            Zambia               & Chlorocebus sabaeus & $ 0.006$              & $ 0.288$                      & $ 0.141$ & $ 0.106$     & $  25.0$      & $ 0.038$ & $ 0.029$ & $  25.3$ \\
            African              & Homo sapiens        & $ 0.003$              & $ 0.243$                      & $ 0.195$ & $ 0.156$     & $  20.2$      & $ 0.038$ & $ 0.026$ & $  32.4$ \\
            Admixed American     & Homo sapiens        & $ 0.002$              & $ 0.242$                      & $ 0.195$ & $ 0.156$     & $  20.2$      & $ 0.038$ & $ 0.026$ & $  31.3$ \\

>>>>

\renewcommand{\thetable}{S\arabic{table}}
\renewcommand{\thefigure}{S\arabic{figure}}

\newcommand{\UniDimArray}[1]{\bm{#1}}
\newcommand{\BiDimArray}[1]{\bm{#1}}
\DeclareMathOperator{\E}{\mathbb{E}}
\DeclareMathOperator{\Var}{\textrm{Var}}
\newcommand{\der}{\textrm{d}}
\newcommand{\e}{\textrm{e}}
\newcommand{\avg}[1]{\left< #1 \right>} % for average
\newcommand{\Ne}{N_{\textrm{e}}}
\newcommand{\proba}{\mathbb{P}}
\newcommand{\pfix}{\proba_{\textrm{fix}}}
\newcommand{\dn}{d_N}
\newcommand{\ds}{d_S}
\newcommand{\dnds}{\dn / \ds}
\newcommand{\Sphy}{S}
\newcommand{\Sphyclass}{\mathcal{C}}
\newcommand{\SphyMean}{\overline{\Sphy}}
\newcommand{\divStrongDel}{\Sphy < -3}
\newcommand{\divDel}{-3 < \Sphy < -1}
\newcommand{\divWeakDel}{-1 < \Sphy < 0}
\newcommand{\divWeakAdv}{0 < \Sphy < 1}
\newcommand{\divAdv}{ \Sphy > 1}
\newcommand{\PdivStrongDel}{\proba \left[ \divStrongDel \right]}
\newcommand{\PdivDel}{\proba \left[ \divDel \right]}
\newcommand{\PdivWeakDel}{\proba \left[ \divWeakDel \right]}
\newcommand{\PdivWeakAdv}{\proba \left[ \divWeakAdv \right]}
\newcommand{\PdivAdv}{\proba \left[ \divAdv \right]}
\newcommand{\given}{\mid}
\newcommand{\Spop}{\beta}
\newcommand{\SpopMean}{\overline{\Spop}}
\newcommand{\polyDel}{\Spop < -1}
\newcommand{\polyNeutral}{-1 < \Spop < 1}
\newcommand{\polyAdv}{ \Spop > 1}
\newcommand{\PpolyDel}{\proba \left[ \polyDel \right]}
\newcommand{\PpolyNeutral}{\proba \left[ \polyNeutral \right]}
\newcommand{\PpolyAdv}{\proba \left[ \polyAdv \right]}

\title{In mammals, an important proportion of advantageous mutations are repairing damaged genomes instead of creating adaptive innovations}

\author{
    \large
    \textbf{T. {Latrille}$^{1}$, J. {Joseph}$^{2}$, N. {Salamin}$^{1}$}\\
    \normalsize $^{1}$Université de Lausanne, Lausanne, Switzerland\\
    \normalsize $^{2}$Université de Lyon, CNRS, LBBE UMR 5558, Villeurbanne, France \\
    \normalsize \texttt{\href{mailto:thibault.latrille@ens-lyon.org}{thibault.latrille@ens-lyon.org}} \\
}

\date{}

@@

    \subsection{Summary tables}\label{subsec:summary-table-mutsel}

    \begin{center}
        \captionof{table}{~}
        \scriptsize
        \begin{longtable*}{|l|l|r|r|r|}
            \toprule
            Population & Species & Tajima $\theta_{\pi}$ & $\mathbb{P}_{div}[\Sphy > 1]$ & $\dn(\Sphy > 1) / \ds$ \\
            \midrule
            \endhead
            \midrule
            \multicolumn{5}{r}{{Continued on next page}} \\
            \midrule
            \endfoot

            \bottomrule
            \endlastfoot
            Equus c. & Equus caballus & $ 0.002$ & $ 0.115$ & $ 1.187$ \\
            Iran & Bos taurus & $ 0.005$ & $ 0.125$ & $ 1.322$ \\
            Uganda & Bos taurus & $ 0.006$ & $ 0.126$ & $ 1.363$ \\
            Australia & Capra hircus & $ 0.003$ & $ 0.122$ & $ 1.035$ \\
            France & Capra hircus & $ 0.004$ & $ 0.122$ & $ 1.043$ \\
            Iran (C. aegagrus) & Capra hircus & $ 0.004$ & $ 0.123$ & $ 1.042$ \\
            Iran & Capra hircus & $ 0.004$ & $ 0.124$ & $ 1.052$ \\
            Italy & Capra hircus & $ 0.004$ & $ 0.122$ & $ 1.037$ \\
            Morocco & Capra hircus & $ 0.004$ & $ 0.124$ & $ 1.057$ \\
            Iran & Ovis aries & $ 0.008$ & $ 0.104$ & $ 1.180$ \\
            Iran (O. orientalis) & Ovis aries & $ 0.009$ & $ 0.103$ & $ 1.187$ \\
            Iran (O. vignei) & Ovis aries & $ 0.008$ & $ 0.104$ & $ 1.172$ \\
            Various & Ovis aries & $ 0.009$ & $ 0.103$ & $ 1.182$ \\
            Morocco & Ovis aries & $ 0.008$ & $ 0.104$ & $ 1.189$ \\
            Barbados & Chlorocebus sabaeus & $ 0.004$ & $ 0.123$ & $ 1.341$ \\
            Central Afr. Rep. & Chlorocebus sabaeus & $ 0.006$ & $ 0.124$ & $ 1.370$ \\
            Ethiopia & Chlorocebus sabaeus & $ 0.005$ & $ 0.124$ & $ 1.361$ \\
            Gambia & Chlorocebus sabaeus & $ 0.005$ & $ 0.124$ & $ 1.359$ \\
            Kenya & Chlorocebus sabaeus & $ 0.006$ & $ 0.125$ & $ 1.371$ \\
            Nevis & Chlorocebus sabaeus & $ 0.004$ & $ 0.124$ & $ 1.349$ \\
            South Africa & Chlorocebus sabaeus & $ 0.007$ & $ 0.126$ & $ 1.391$ \\
            Saint Kitts & Chlorocebus sabaeus & $ 0.004$ & $ 0.125$ & $ 1.362$ \\
            Zambia & Chlorocebus sabaeus & $ 0.006$ & $ 0.124$ & $ 1.362$ \\
            African & Homo sapiens & $ 0.003$ & $ 0.104$ & $ 1.475$ \\
            Admixed American & Homo sapiens & $ 0.002$ & $ 0.103$ & $ 1.466$ \\
            East Asian & Homo sapiens & $ 0.002$ & $ 0.104$ & $ 1.478$ \\
            European & Homo sapiens & $ 0.002$ & $ 0.103$ & $ 1.461$ \\
            South Asian & Homo sapiens & $ 0.002$ & $ 0.104$ & $ 1.473$ \\
        \end{longtable*}
    \end{center}
    \begin{itemize}
        \item Tajima $\theta$ is the synonymous diversity.
        \item $\mathbb{P}_{div}[\Sphy > 1]$ is the proportion of substitutions in the terminal branch observed with a selection coefficient at the phylogenetic scale larger than 1 ($\Sphy > 1$).
        \item $\dn(\Sphy > 1) / \ds$ is the ratio of non-synonymous over synonymous divergence (also called $\dnds$) estimated for the non-synonymous substitutions in the terminal branch with a selection coefficient larger than 1 ($\Sphy > 1$).
    \end{itemize}

    \newpage
    \begin{center}
        \captionof{table}{~}
        \scriptsize
        \begin{longtable*}{|l|l|r|r|r|r|r|r|}
            \toprule
            Population & Species & Tajima $\theta_{\pi}$ & $\mathbb{P}[\Sphy > 1]$ & $\mathbb{P} [ \Spop > 1 ]$ & $\frac{\mathbb{P}[\Sphy > 1]}{\mathbb{P}[ \Spop > 1 ]}$ & $\mathbb{P} [ \Spop > 1 \given \Sphy > 1]$ & $\mathbb{P}[\Sphy > 1\given \Spop > 1 ]$ \\
            \midrule
            \endhead
            \midrule
            \multicolumn{8}{r}{{Continued on next page}} \\
            \midrule
            \endfoot

@@

            Equus c. & Equus caballus & $ 0.002$ & $ 0.018$ & $ 0.042$ & $ 0.443$ & $ 0.404$ & $ 0.179$ \\
            Iran & Bos taurus & $ 0.005$ & $ 0.017$ & $ 0.036$ & $ 0.471$ & $ 0.368$ & $ 0.173$ \\
            Uganda & Bos taurus & $ 0.006$ & $ 0.017$ & $ 0.035$ & $ 0.490$ & $ 0.369$ & $ 0.181$ \\
            Australia & Capra hircus & $ 0.003$ & $ 0.017$ & $ 0.036$ & $ 0.488$ & $ 0.144$ & $ 0.070$ \\
            France & Capra hircus & $ 0.004$ & $ 0.017$ & $ 0.034$ & $ 0.515$ & $ 0.168$ & $ 0.086$ \\
            Iran (C. aegagrus) & Capra hircus & $ 0.004$ & $ 0.017$ & $ 0.035$ & $ 0.493$ & $ 0.093$ & $ 0.046$ \\
            Iran & Capra hircus & $ 0.004$ & $ 0.017$ & $ 0.030$ & $ 0.589$ & $ 0.140$ & $ 0.083$ \\
            Italy & Capra hircus & $ 0.004$ & $ 0.017$ & $ 0.032$ & $ 0.545$ & $ 0.150$ & $ 0.081$ \\
            Morocco & Capra hircus & $ 0.004$ & $ 0.017$ & $ 0.029$ & $ 0.598$ & $ 0.137$ & $ 0.082$ \\
            Iran & Ovis aries & $ 0.008$ & $ 0.018$ & $ 0.022$ & $ 0.802$ & $ 0.046$ & $ 0.037$ \\
            Iran (O. orientalis) & Ovis aries & $ 0.009$ & $ 0.018$ & $ 0.025$ & $ 0.718$ & $ 0.071$ & $ 0.051$ \\
            Iran (O. vignei) & Ovis aries & $ 0.008$ & $ 0.018$ & $ 0.028$ & $ 0.642$ & $ 0.220$ & $ 0.141$ \\
            Various & Ovis aries & $ 0.009$ & $ 0.018$ & $ 0.024$ & $ 0.748$ & $ 0.108$ & $ 0.081$ \\
            Morocco & Ovis aries & $ 0.008$ & $ 0.018$ & $ 0.020$ & $ 0.883$ & $ 0.070$ & $ 0.062$ \\
            Barbados & Chlorocebus sabaeus & $ 0.004$ & $ 0.015$ & $ 0.040$ & $ 0.375$ & $ 0.374$ & $ 0.140$ \\
            Central Afr. Rep. & Chlorocebus sabaeus & $ 0.006$ & $ 0.015$ & $ 0.034$ & $ 0.435$ & $ 0.368$ & $ 0.160$ \\
            Ethiopia & Chlorocebus sabaeus & $ 0.005$ & $ 0.015$ & $ 0.040$ & $ 0.377$ & $ 0.368$ & $ 0.139$ \\
            Gambia & Chlorocebus sabaeus & $ 0.005$ & $ 0.015$ & $ 0.031$ & $ 0.482$ & $ 0.377$ & $ 0.182$ \\
            Kenya & Chlorocebus sabaeus & $ 0.006$ & $ 0.015$ & $ 0.035$ & $ 0.428$ & $ 0.308$ & $ 0.132$ \\
            Nevis & Chlorocebus sabaeus & $ 0.004$ & $ 0.015$ & $ 0.037$ & $ 0.404$ & $ 0.368$ & $ 0.149$ \\
            South Africa & Chlorocebus sabaeus & $ 0.007$ & $ 0.015$ & $ 0.034$ & $ 0.435$ & $ 0.368$ & $ 0.160$ \\
            Saint Kitts & Chlorocebus sabaeus & $ 0.004$ & $ 0.015$ & $ 0.039$ & $ 0.388$ & $ 0.368$ & $ 0.143$ \\
            Zambia & Chlorocebus sabaeus & $ 0.006$ & $ 0.015$ & $ 0.038$ & $ 0.392$ & $ 0.368$ & $ 0.144$ \\
            African & Homo sapiens & $ 0.003$ & $ 0.015$ & $ 0.038$ & $ 0.403$ & $ 0.604$ & $ 0.243$ \\
            Admixed American & Homo sapiens & $ 0.002$ & $ 0.015$ & $ 0.037$ & $ 0.409$ & $ 0.574$ & $ 0.235$ \\
            East Asian & Homo sapiens & $ 0.002$ & $ 0.015$ & $ 0.036$ & $ 0.426$ & $ 0.484$ & $ 0.206$ \\
            European & Homo sapiens & $ 0.002$ & $ 0.015$ & $ 0.037$ & $ 0.414$ & $ 0.517$ & $ 0.214$ \\
            South Asian & Homo sapiens & $ 0.002$ & $ 0.015$ & $ 0.036$ & $ 0.428$ & $ 0.532$ & $ 0.227$ \\

@@

        \item $\mathbb{P} [ \Sphy > 1 ]$ is the probability for a new mutation to be under maintenance selection.
        These mutations have a selection coefficient predicted at the phylogenetic-scale larger than 1 ($\Sphy > 1$), thus toward a more fit amino-acid.
        In other words, this probability is the part of the DFE estimated by mutation-selection models greater than 1.
        \item $\mathbb{P} [ \Spop > 1 ]$ is the probability for a mutation to be positively selected.
        These mutations have a selection coefficient at the population-scale larger than 1 ($\Spop > 1$), estimated from all SNPs in the population.
        In other words, this probability is the part of the DFE estimated by polyDFE greater than 1.
        \item $\mathbb{P} [ \Spop > 1 \given \Sphy > 1]$ is the probability for a mutation to be positively selected, given it is under maintenance selection.
        These mutations have a selection coefficient at the population-scale larger than 1 ($\Spop > 1$), estimated by polyDFE on the SNPs with a predicted selection coefficient larger than 1 ($\Sphy > 1$).
        In other words, this probability is the part of the DFE estimated by polyDFE greater than 1, when we restricted our analysis on SNPs that are already predicted by mutation-selection models to have a selection coefficient greater than 1.
        \item $\mathbb{P} [ \Sphy > 1 \given \Spop > 1]$ is the probability for a mutation to be under maintenance selection, given it is positively selected.
        This probability is obtained using Bayes' formula.

@@

%    \begin{center}
%        \captionof{table}{~}
%        \scriptsize
%        \begin{longtable*}{|l|l|r|r|r|r|r|r|}
%            \toprule
%            Population & Species & Tajima $\theta_{\pi}$ & $\mathbb{P}[\Sphy > 0]$ & $\mathbb{P} [\Spop > 0 ]$ & $\frac{\mathbb{P}[\Sphy > 0]}{\mathbb{P}[\Spop > 0]}$ & $\mathbb{P} [\Spop > 0 \given \Sphy > 0]$ & $\mathbb{P}[\Sphy > 0|\Spop > 0]$ \\
%            \midrule
%            \endhead
%            \midrule
%            \multicolumn{8}{r}{{Continued on next page}} \\
%            \midrule
%            \endfoot
%%
%            \bottomrule
%            \endlastfoot
%            Equus c. & Equus caballus & $ 0.002$ & $ 0.054$ & $ 0.113$ & $ 0.473$ & $ 0.489$ & $ 0.231$ \\
%            Iran & Bos taurus & $ 0.005$ & $ 0.053$ & $ 0.098$ & $ 0.540$ & $ 0.368$ & $ 0.198$ \\
%            Uganda & Bos taurus & $ 0.006$ & $ 0.053$ & $ 0.094$ & $ 0.558$ & $ 0.419$ & $ 0.234$ \\
%            Australia & Capra hircus & $ 0.003$ & $ 0.054$ & $ 0.096$ & $ 0.557$ & $ 0.126$ & $ 0.070$ \\
%            France & Capra hircus & $ 0.004$ & $ 0.054$ & $ 0.092$ & $ 0.583$ & $ 0.297$ & $ 0.173$ \\
%            Iran (C. aegagrus) & Capra hircus & $ 0.004$ & $ 0.054$ & $ 0.096$ & $ 0.561$ & $ 0.080$ & $ 0.045$ \\
%            Iran & Capra hircus & $ 0.004$ & $ 0.054$ & $ 0.080$ & $ 0.667$ & $ 0.281$ & $ 0.188$ \\
%            Italy & Capra hircus & $ 0.004$ & $ 0.054$ & $ 0.087$ & $ 0.617$ & $ 0.304$ & $ 0.187$ \\
%            Morocco & Capra hircus & $ 0.004$ & $ 0.054$ & $ 0.079$ & $ 0.679$ & $ 0.131$ & $ 0.089$ \\
%            Iran & Ovis aries & $ 0.008$ & $ 0.054$ & $ 0.060$ & $ 0.897$ & $ 0.304$ & $ 0.273$ \\
%            Iran (O. orientalis) & Ovis aries & $ 0.009$ & $ 0.054$ & $ 0.067$ & $ 0.806$ & $ 0.345$ & $ 0.278$ \\
%            Iran (O. vignei) & Ovis aries & $ 0.008$ & $ 0.054$ & $ 0.075$ & $ 0.720$ & $ 0.464$ & $ 0.334$ \\
%            Various & Ovis aries & $ 0.009$ & $ 0.054$ & $ 0.064$ & $ 0.840$ & $ 0.359$ & $ 0.302$ \\
%            Morocco & Ovis aries & $ 0.008$ & $ 0.054$ & $ 0.055$ & $ 0.971$ & $ 0.247$ & $ 0.240$ \\
%            Barbados & Chlorocebus sabaeus & $ 0.004$ & $ 0.050$ & $ 0.109$ & $ 0.463$ & $ 0.350$ & $ 0.162$ \\
%            Central Afr. Rep. & Chlorocebus sabaeus & $ 0.006$ & $ 0.050$ & $ 0.094$ & $ 0.537$ & $ 0.225$ & $ 0.121$ \\
%            Ethiopia & Chlorocebus sabaeus & $ 0.005$ & $ 0.050$ & $ 0.108$ & $ 0.466$ & $ 0.312$ & $ 0.145$ \\
%            Gambia & Chlorocebus sabaeus & $ 0.005$ & $ 0.050$ & $ 0.084$ & $ 0.602$ & $ 0.286$ & $ 0.172$ \\
%            Kenya & Chlorocebus sabaeus & $ 0.006$ & $ 0.050$ & $ 0.095$ & $ 0.529$ & $ 0.196$ & $ 0.104$ \\
%            Nevis & Chlorocebus sabaeus & $ 0.004$ & $ 0.050$ & $ 0.101$ & $ 0.500$ & $ 0.296$ & $ 0.148$ \\
%            South Africa & Chlorocebus sabaeus & $ 0.007$ & $ 0.050$ & $ 0.094$ & $ 0.534$ & $ 0.243$ & $ 0.130$ \\
%            Saint Kitts & Chlorocebus sabaeus & $ 0.004$ & $ 0.050$ & $ 0.106$ & $ 0.473$ & $ 0.309$ & $ 0.146$ \\
%            Zambia & Chlorocebus sabaeus & $ 0.006$ & $ 0.050$ & $ 0.104$ & $ 0.485$ & $ 0.245$ & $ 0.119$ \\
%            African & Homo sapiens & $ 0.003$ & $ 0.051$ & $ 0.103$ & $ 0.497$ & $ 0.785$ & $ 0.390$ \\
%            Admixed American & Homo sapiens & $ 0.002$ & $ 0.051$ & $ 0.104$ & $ 0.492$ & $ 0.737$ & $ 0.363$ \\
%            East Asian & Homo sapiens & $ 0.002$ & $ 0.051$ & $ 0.098$ & $ 0.521$ & $ 0.684$ & $ 0.356$ \\
%            European & Homo sapiens & $ 0.002$ & $ 0.051$ & $ 0.097$ & $ 0.526$ & $ 0.687$ & $ 0.361$ \\
%            South Asian & Homo sapiens & $ 0.002$ & $ 0.051$ & $ 0.096$ & $ 0.530$ & $ 0.691$ & $ 0.366$ \\
%        \end{longtable*}
%    \end{center}
%    \begin{itemize}
%        \item Tajima $\theta$ is the synonymous diversity.
%        \item $\mathbb{P} [ \Sphy > 0 ]$ is the probability for a new mutation to be under maintenance selection.
%        These mutations have a positive selection coefficient predicted at the phylogenetic-scale larger ($\Sphy > 0$), thus toward a more fit amino-acid.
%        In other words, this probability is the positive part of the DFE estimated by mutation-selection models.
%        \item $\mathbb{P} [ \Spop > 0 ]$ is the probability for a mutation to be positively selected.
